\emeszida

### 2024-03-29 sigbovik/paper.tex
Add authors

\author{First Author \\
  Affiliation / Address line 1 \\
  Affiliation / Address line 2 \\
  Affiliation / Address line 3 \\
  \texttt{email@domain} \\\And
  Second Author \\
  Affiliation / Address line 1 \\
  Affiliation / Address line 2 \\
  Affiliation / Address line 3 \\
  \texttt{email@domain} \\}

>>>>

\author{\\
    \begin{tabular}{c}
    M. Willis Monroe$^1$\\
    {\tt\small willis.monroe@ubc.ca}
    \end{tabular}
    \begin{tabular}{c}
    Logan Born$^2$\\
    {\tt\small loborn@sfu.ca}
    \end{tabular}
    \begin{tabular}{c}
    Kathryn Kelley$^3$\\
    {\tt\small kathrynerin.kelley@unibo.it}
    \end{tabular}
    \begin{tabular}{c}
    Anoop Sarkar$^2$\\
    {\tt\small anoop@cs.sfu.ca}
    \end{tabular}\\[12pt]
    \begin{tabular}{c}
         $^1$University of British Columbia\\
         Department of Philosophy
    \end{tabular} $\quad$
    \begin{tabular}{c}
         $^2$Simon Fraser University\\
         School of Computing Science
    \end{tabular}\\[12pt]
    \begin{tabular}{c}
         $^3$Universit\`a di Bologna\\
         Dipartimento di Filologia Classica e Italianistica
    \end{tabular} \\[12pt]
}
